
\documentclass{resume} 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arya Stark} % Your name
\address{Winerfell "Game of Thrones"} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Syrio Forel} \hfill {\em Season 1}
\\Bachelor of The art of combat



{\bf The House of Black and White} \hfill {\em Season 5} 
\\Bachelor of The fight skills 
\\Master of Changing faces 


\end{rSection}

\begin{rSection}{Carrier Objective}
Looking forwards to work for an organization which can help me improve my combat skills and help me to be stronger. Revenge for my families is my primary career goal.
\end{rSection}
%--------------------------------------------------------------------------------
%    Killing Projects 
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Killing Projects}
{\bf Meryn Trant}
\\The project aims at revenging for my first teacher, Syrio Forel. Finished by slitting Meryn's throat fast and quietly.

{\bf The Waif}\\
Suffered from major pains from this project. Hurting badly during The Waif's hunt. Battled in the darkness and successfully fight back and survived from the fight.

{\bf Walder Frey and his family}\\
Walder Frey is the leader of murdering my mother, brother, and sister-in-law. Disguised as a serving girl, poisoned the whole Frey's family, slit Walder Frey's throat to finishing another major steps of revenging.

{\bf Petyr}\\
Petyr, Little Finger, who is the responsible person of my father, Ned Stark's death. Killed him under Sansa Stark's order. 


\end{rSection}
%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Water of Dance \\
Perfect Combat Skills \\
Changing Faces \\
Close Distance killing and Fighting \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{The House of Black and White}{Season 6}{Killer}{}
\item On-site part time under famous killer organization. Learned and implemented various aspects as changing faces and voice, safety precautions, precises killing target, and fighting skills. 
\end{rSubsection}


\end{rSection}


%	HABITS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Habits} 
\item Practicing fighting with sword
\item Spending time with my dogs
\item Revenging for the Stark's family
\end{rSection}


\end{document}
